Early environmental conditions do not impact behavioural flexibility in an invasive and non-invasive lizard species

### 2024-05-17 ms.qmd
Updates

---
title: "Early environmental conditions do not impact behavioural flexibility in an invasive and non-invasive lizard species"
format:
  docx: 
    bibliography: "./bib/refs.bib"
    csl: "./bib/biology-letters.csl"
    reference-doc: "./bib/tmpl.docx"
execute:
  echo: false
  error: false
  cache: false
  warning: false
link-citations: true
crossref:  
  fig-title: Fig    # (default is "Figure")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Table  # (default is "Table")
editor_options: 
  chunk_output_type: console
---

@@

Pablo Recio-Santiago^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi L. Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^

@@

Novel environments faced by invasive populations introduce organisms to a plethora of unfamiliar and potentially stressful situations. Sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses  that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000]. Glucocorticoids can be transmitted to offspring and influence their phenotype and development through transgenerational effects [@Crino_2023]. In addition to novel environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects. Temperature, in particular, is likely to deviate in invasive populations compared to source populations, having a direct effect on offspring phenotypes with long-lasting consequences [@noble_developmental_2018]. As such, GCs and temperature are predicted to interact to influence the offspring phenotype with particularly potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic]. While behavioural flexibility is recognised as an important behavioural phenotype for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can], we know little about how novel environmental stressors, such as GCs or temperature, impact behavioural flexibility. Such knowledge is crucial for understanding the potential for invasive populations to adapt to new environments and the potential for invasion success.

Here, we studied the effects of prenatal temperature and the glucocorticoid, corticosterone (CORT) (the main GC in reptiles) [@Crino_2023], on behavioural flexibility in two species with distinct histories of invasion success, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). _Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], but the same is not true of _L. guichenoti_ despite the two species having similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014]. Personality has been shown to be different between these two species [@chapple_know_2011; @chapple2012can; @bezzina2014does], which could be related to general cognitive differences that are important for invasion success. Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but the interactive role of maternal CORT and early temperatures has not yet been explored. Differences in the relative impact of early environments on behavioural flexibility may help explain differing invasion success between the two species. We predict that _L. delicata_, on average, will perform more proficiently in the task compared to _L. guichenoti_. We also anticipate prenatal CORT and temperature to affect the behavioural flexibility of both species, and that _L. guichenoti_ will be more impacted by the prenatal environment than _L. delicata_.

@@

#### Manipulating Early Thermal and CORT Environments  
To manipulate early thermal environment and CORT, we collected eggs of _L. delicata_ and _L. guichenoti_ from a lab breeding colony that was established from a Sydney population in 2019. The Sydney population is thought to be the source population for invasive populations established on Lord Howe Island [@chapple2016origin]. Eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (CORT treatment) or the same volume of the vehicle (Control) and were then incubated at different temperatures (Cold – 23ºC ± 3ºC or Hot – 30ºC ± 3ºC) until hatching in a fully factorial design. For full details of breeding colony and husbandry see Supplementary Material.

#### Quantifying Behavioural Flexibility  
Briefly, the learning test was divided in three main phases: a habituation phase where lizards had to learn to eat a frozen-thawed cricket from white 3D-printed polylactic acid (PLA) ramps (9 L x 4 W x 5 H cm). The habituation phase lasted 38 days. This was followed by a colour association task where lizards had to associate the food reward with one of two colours (red or blue) (@fig-Methods Associative task). The associative learning task lasted 35 days. Finally, to quantify behavioural flexibility, we reversed the previously trained colour (red or blue) so that the lizards needed to learn to associate the food with the opposite colour (@fig-Methods Reversal task). The reversal learning task lasted a total of 40 days. Lizards were tested once daily between 11 am to 12 pm when they were most active.

In associative and reversal tasks we used three different ramps that were identical in size and shape to the ones used in the habituation phase. The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. To avoid the influence of chemical cues, we placed the food reward in all three ramps, but in two of them the cricket was covered by immovable small lids with holes on the top. To control for potential colour biases, we assigned one group of lizards within each treatment to associate food in the blue ramp followed by the red ramp in the reversal, while in the other group the order was reversed. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association.

We recorded whether the animal chose the correct ramp first or not. We considered that a choice was made if the head of the lizard was inside the well of one of the ramps. We considered a trial failed if there was no choice in one hour of recording and those trials were scored as NA. Here, we analysed the data of the reversal task as a measure of behavioural flexibility [@brown2010behavioral].

@@

#### Statistical analyses  
We performed the analyses for each species separately. We fitted two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using an R extension (version 2.8.2) [@R]. We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations. We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and their interaction as fixed factors. We included a random intercept and slope (trial) for each lizard in our models. We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species. Learning slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments. Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not. We calculated the probability that slopes or contrasts between slopes differed from zero (p~mcmc~) using the posterior distributions. We considered statistical significance if p~mcmc~  < 0.05.

@@

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## A) L. delicata
deli <- fit_m(clean_df, "deli", "complete",  refit = FALSE)
write.csv(deli, file= "./output/Checking/deli.csv")
## B) L. guichenoti
guich <- fit_m(clean_df, "guich", "complete", refit = FALSE)
write.csv(guich, file= "./output/Checking/guich.csv")
```

@@

*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above). We checked for the presence of eggs in the boxes three days a week. After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weighed them with a (OHAUS, Model spx123) digital scale ± 0.001g error. Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite). The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.

###### CORT and Temperature manipulation  
To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A). We first allocated eggs to one of two different treatments: CORT treatment, where eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final (10 pg CORT/mL) concentration (CORT treatment); and a Control treatment, where eggs received an equal volume of the vehicle. CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data). Then, eggs were incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching. The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.

###### Learning task
The habituation phase was divided into three stages: in the first stage, the reward, a small, frozen cricket (*A. domestica*) was placed in an opaque petri dish (3D x 1.6H cm) (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and in the third stage, the cricket was left inside a well (3D x 1.75H cm) on top of the ramp (Fig. @fig-Methods B, Stage 3). Trials in every stage lasted one hour, begining when the feeding block (petri dish, ramp, or both) was placed inside the enclosure and finished when we took the feeding block away. We recorded whether the cricket had been consumed or not and we considered a stage as completed if the lizards ate the crickets in at least 5 out of 6 trials. This phase lasted 38 days, and only in one case we decided not to use the lizard in the next phases because its behaviour was not consistent.  
In the associative phase, we used three ramps that were identical in shape and size but differ in the colour (Associative task in Fig. @fig-Methods B). As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp. The food reward was placed in all three wells to avoid lizards using prey chemical cues, that were released in the closed wells through a series of small holes on the top of the lids. The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. However, we decided to split the lizards in two groups to control for potential colour preference that could bias our results. One group of lizards was assigned the blue ramp as the correct choice (i.e., the ramp with the non-covered frozen cricket) in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. Lizards were tested in this task once a day for 35 days. After the colour association phase, we performed a choice reversal task (Reversal task in @fig-Methods B). Here, the attainability of prey was indicated by a different colour from the reversal, requiring the lizards to form a novel association between the new colour and the food reward. This test was done once a day for 40 days.

We performed the full experiment between the 6^th^ of March until the 26^th^ of June 2023, between 11 to 12 am, when the lizards were active. Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual. Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not. We considered a choice was made if the head of the lizard was inside the well of one of the ramps. We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses. We excluded from our analyses those individuals with more than 15 trials failed (i.e. they did not make a choice), and we considered the first trial to be the first one where the individual made a choice. We also considered individuals to be reinforced if the cricket was eaten after the test independently of whether their initial choice was correct or not.

@@

```{r, models2}
#| label: models2
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## A) L. delicata
deli_2 <- fit_m(clean_df_2, "deli", "suppl", refit = FALSE)
write.csv(deli_2, file= "./output/Checking/deli.csv")
## B) L. guichenoti
guich_2 <- fit_m(clean_df_2, "guich", "suppl", refit = FALSE)
write.csv(guich_2, file= "./output/Checking/guich.csv")
```

@@

Model formula: 
Choice ~ age.start + trial_associative * cort * temp + (1 + trial_associative|lizard_id)

```{r, modelsage}
#| label: modelsage
# Fitting the models for L. delicata and L. guichenoti including age as a covariate
#
data_age <- clean_df %>%
  mutate(age.start = as.numeric(age.start)-mean(as.numeric(age.start)))
refit2 = FALSE
formula <- FC_reversal ~ age.start + trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
species <- c("delicata", "guichenoti")
#
models <- list() # Create an empty list to store the models
for(s in species){
  # Subset the data for the species
  data_species <- data_age %>%
    filter(species == s)
  # Define model file name
  model_file <- paste0("output/models/model_age_", s, ".rds")
# Fit the model only if it has not been fit yet (if refit2 = TRUE)
  if(refit2){
    # Fit the model
    model <- brm(formula,
                data = data_species,
                family = bernoulli(link = "logit"),
                chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99))
    # Write the model to a file
    saveRDS(model, file = model_file)
  } else {
      # Read the model from a file
      model <- readRDS(file = model_file)
  }
  # Save the model to the list
  models[[s]] <- model
}
model_age_deli <- models[["delicata"]]
model_age_guich <- models[["guichenoti"]]
```

>>>>

---
title: "Early environmental conditions do not impact behavioural flexibility in an invasive and non-invasive lizard species"
format:
  docx: 
    bibliography: "./bib/refs.bib"
    csl: "./bib/animal-behaviour.csl"
    reference-doc: "./bib/tmpl.docx"
execute:
  echo: false
  error: false
  cache: false
  warning: false
link-citations: true
crossref:  
  fig-title: Fig    # (default is "Figure")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Table  # (default is "Table")
editor_options: 
  chunk_output_type: console
---

@@

Pablo Recio^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi L. Crino ^1,2^, Kristoffer H. Wild^1,3^, Chris Friesen^4^, Basile Mauclaire^1,5^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^

@@

Novel environments faced by invasive populations introduce organisms to a plethora of unfamiliar and potentially stressful situations. Sensory systems detect and transmit environmental signals to instigate adaptive physiological and behavioural adjustments – responses  that are mediated by glucocorticoids (GCs) [@sapolsky_how_2000]. Glucocorticoids can be transmitted to offspring and influence their phenotype and development through transgenerational effects [@Crino_2023]. In addition to novel environments experienced by parents, offspring also experience potentially stressful environmental conditions that can interact with or amplify parental effects. Temperature, in particular, is likely to deviate in invasive populations compared to source populations, with direct effect on offspring phenotypes with long-lasting consequences in ectotherms [@noble_developmental_2018]. As such, GCs and temperature are predicted to interact to influence the offspring phenotype with particularly potent effects on brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017] and cognition [@clark_colour_2014; @lui2017chronic]. While behavioural flexibility is recognised as an important behavioural phenotype for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can], we know little about how novel environmental stressors, such as GCs or temperature, impact behavioural flexibility. Such knowledge is crucial for understanding the potential for invasive populations to adapt to new environments and the potential for invasion success.

Here, we studied the effects of prenatal temperature and the glucocorticoid, corticosterone (CORT) (the main GC in reptiles) [@Crino_2023], on behavioural flexibility in two species with distinct histories of invasion success, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). _Lampropholis delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], but the same is not true of _L. guichenoti_ despite the two species having similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014]. Personality has been shown to be different between these two species [@chapple_know_2011; @chapple2012can; @bezzina2014does], which could be related to general cognitive differences like learning (**REF**) that are important for invasion success. Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [@carrasco2023maternal; @kar2023heritability], but the interactive role of maternal CORT and early temperatures has not yet been explored. Differences in the relative impact of early environments on behavioural flexibility may help explain differing invasion success between the two species. We predict that _L. delicata_, on average, will perform more proficiently in the task compared to _L. guichenoti_. We also anticipate prenatal CORT and temperature to affect the behavioural flexibility of both species, and that _L. guichenoti_ will be more impacted by the prenatal environment than _L. delicata_. More specifically, we predicted cold incubation temperatures and CORT treatment to impair behavioural flexibility (**REFs**), and that the combination of both treatments would have the most detrimental effect on behavioural flexibility.

@@

*Eggs collection and incubation* -- Between mid-October 2022 to the end of February 2023, we provided females with a place to lay the eggs by means of small boxes (12.5 L x 8.3 W x 5 H cm) with moist vermiculite inside, that were placed in one extreme of the communal enclosures (see above). We checked for the presence of eggs in the boxes three days a week. After collection, we measured length and width of eggs with a digital caliper to the nearest 0.1 mm and weighed them with a (OHAUS, Model spx123) digital scale ± 0.001g error, and we recorded the clutch and egg identities. Then eggs were treated with CORT or vehicle (see CORT and Temperature manipulation below) and were placed in individual cups (80 mL) with moist vermiculite (12 parts water to 4 parts vermiculite). The cups were covered with cling wrap to retain moisture and left in LATWIT 2X5D-R1160 incubators at two different temperatures (see CORT and Temperature manipulation below) until hatching.

#### Manipulating Early Thermal and CORT Environments

To test empirically the effect of early environment we manipulated CORT concentration in eggs and incubated them under one of two temperature regimes (Cold -- 23ºC ± 3ºC or Hot -- 30ºC ± 3ºC) in a 2x2 factorial design (@fig-Methods A). We first allocated eggs to one of two different treatments: in the CORT treatment, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol (vehicle) at a final (10 pg CORT/mL) concentration; in the Control treatment eggs received an equal volume of the vehicle. CORT concentration employed in the CORT treatment represents 2 standard deviations above the mean natural concentration obtained in eggs from both species (non-published data). Then, eggs were incubated in one of the two previously mentioned temperature regimes (Cold or Hot) until hatching. This temperatures represent the upper and lower limit of the natural incubation temperatures [**REF**]. The number of eggs per clutch assigned to each hormone and temperature treatment were counterbalanced in both species.

#### Quantifying Behavioural Flexibility  
Briefly, the learning test was divided in three main phases: a habituation phase where lizards had to learn to eat a frozen-thawed cricket from white 3D-printed polylactic acid (PLA) ramps (9 L x 4 W x 5 H cm); a colour association task where lizards had to associate the food reward with one of two colours (red or blue) (@fig-Methods Associative task); and finally, to quantify behavioural flexibility, we reversed the previously trained colour (red or blue) so that the lizards needed to learn to associate the food with the opposite colour (@fig-Methods Reversal task).

The habituation phase was divided into three stages: in the first stage, the reward, a small, frozen cricket (*A. domestica*) was placed in an opaque petri dish (3D x 1.6H cm) (@fig-Methods Habituation phase, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods Habituation phase, Stage 2); and in the third stage, the cricket was left inside a well (3D x 1.75H cm) on top of the ramp (Fig. @fig-Methods Habituation phase, Stage 3). Trials in every stage lasted one hour, begining when the feeding block (petri dish, ramp, or both) was placed inside the enclosure and finishing when we took the feeding block away. We recorded whether the cricket had been consumed or not and we considered a stage as completed if the lizards ate the crickets in at least 5 out of 6 trials. This phase lasted 38 days, and only in one case we decided not to use the lizard in the next phases because it did not pass the aqcuisition criterium.

In the colour association (Associative task in Fig. @fig-Methods) and reversal task (Reversal task in @fig-Methods B), we used three ramps that were identical in shape and size but differ in the colour. The colours of these ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. However, to control for potential colour biases, we assigned one group of lizards within each treatment to associate food in the blue ramp followed by the red ramp in the reversal, while in the other group the order was reversed. As in the last stage of the habituation phase, we placed the cricket inside the wells of the ramps, but then two of them were covered with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp. The food reward was placed in all three ramps to avoid lizards using prey chemical cues, that were released in the closed wells through a series of small holes on the top of the lids. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. Lizards were tested in the association task once a day for 35 days and once a day for 40 days in teh reversal.

The full experiment was performed between the 6^th^ of March until the 26^th^ of June 2023. Tests were made between 11 to 12 am, when the lizards were active. Trials in the learning phases (colour associative task and reversal tasks) were recorded with different CCTV systems always using the same camera per individual. We recorded whether the animal chose the correct ramp first or not. We considered that a choice was made if the head of the lizard was inside the well of one of the ramps. We considered a trial failed if there was no choice in one hour of recording and those trials were scored as NA. Here, we analysed the data of the reversal task as a measure of behavioural flexibility [@brown2010behavioral].

@@

#### Statistical analyses  
We performed the analyses for each species separately. We fitted two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using an R extension (version 2.8.2) [@R]. We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations. We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and their interaction as fixed factors. We included a random intercept and slope (trial) for each lizard in our models. We also incorporated the clutch identity as a random factor. We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species. Learning slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments. Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not. We calculated the probability that slopes or contrasts between slopes differed from zero (p~mcmc~) using the posterior distributions. We considered statistical significance if p~mcmc~  < 0.05.

@@

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id) + (1|clutch)
## A) L. delicata
deli <- fit_m(clean_df, "deli", "complete",  refit = FALSE)
write.csv(deli, file= "./output/Checking/deli.csv")
## B) L. guichenoti
guich <- fit_m(clean_df, "guich", "complete", refit = FALSE)
write.csv(guich, file= "./output/Checking/guich.csv")
```

@@

@@

```{r, models2}
#| label: models2
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id) + (1|clutch)
## A) L. delicata
deli_2 <- fit_m(clean_df_2, "deli", "suppl", refit = FALSE)
write.csv(deli_2, file= "./output/Checking/deli.csv")
## B) L. guichenoti
guich_2 <- fit_m(clean_df_2, "guich", "suppl", refit = FALSE)
write.csv(guich_2, file= "./output/Checking/guich.csv")
```

@@

Model formula: 
Choice ~ age.start + trial_associative * cort * temp + (1 + trial_associative|lizard_id) + (1|clutch)

```{r, modelsage}
#| label: modelsage
# Fitting the models for L. delicata and L. guichenoti including age as a covariate
#
data_age <- clean_df %>%
  mutate(age.start = as.numeric(age.start)-mean(as.numeric(age.start)))
refit2 = FALSE
formula <- FC_reversal ~ age.start + trial_reversal*cort*temp + (1 + trial_reversal|lizard_id) + (1|clutch)
species <- c("delicata", "guichenoti")
#
models <- list() # Create an empty list to store the models
for(s in species){
  # Subset the data for the species
  data_species <- data_age %>%
    filter(species == s)
  # Define model file name
  model_file <- paste0("output/models/model_age_", s, ".rds")
# Fit the model only if it has not been fit yet (if refit2 = TRUE)
  if(refit2){
    # Fit the model
    model <- brm(formula,
                data = data_species,
                family = bernoulli(link = "logit"),
                chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99))
    # Write the model to a file
    saveRDS(model, file = model_file)
  } else {
      # Read the model from a file
      model <- readRDS(file = model_file)
  }
  # Save the model to the list
  models[[s]] <- model
}
model_age_deli <- models[["delicata"]]
model_age_guich <- models[["guichenoti"]]
```
